---
title: "EPI 590R Final"
format: html
editor: visual
theme: cosmo
---

## **Obstetrics and Periodontal Therapy Data Set**

This study was a randomized controlled study conducted to determine if nonsurgical periodontal treatment given to women before 21 weeks gestation compared to after delivery was linked to better preterm birth and low birth weight outcomes. Participants diagnosed with maternal periodontal disease from four centers were randomly assigned to the treatment and control groups, with data being collected at visits 1, 3, and 5. This data was obtained from the medicaldata repository from user "higgi13425" (https://github.com/higgi13425/medicaldata/tree/master/data).

@tbl-one produces the Descriptive Statistics of the study group, stratified by the origin of the clinic participants were recruited from. There are `r inline_text(table1, variable="Asian", level="Yes", column="NY")` people who were Asian and from the New York clinic in this study.

```{r}
#| label: tbl-one
#| tbl-cap: "Descriptive Statistics"
#| output-location: slide
table1<-tbl_summary(
	opt,
	by=Clinic,
	include=c(Group, Age, Black, White, Nat.Am, Asian, Hisp, Education
	))
table1
```

```{r}
#| label: tbl-two
#| tbl-cap: "Regression Statistics"
#| output-location: slide
table2<-logistic_model<-glm(Group~Age+Education, data=opt, family = binomial())
tbl_regression(
	logistic_model,
	exponentiate =TRUE,
	label = list(
		Age ~ "Age of Women",
		Education ~ "Level of Education"
	))
table2
```

The average age of study participants was `r round(age_avg, 1)` and the oldest particpant in this study was 44 from Minnesota, as @fig1 shows.

```{r}
#| label: fig1
#| boxplot-cap: "Figure 1"
#| output-location: slide
bp<-boxplot(opt$Age~opt$Clinic,
				xlab="Clinic",
				ylab="Age",
				main="Participants Ages by Clinic")
bp
age_avg<-mean(opt$Age, na.rm=TRUE)
```
